---
title: "2015 Shooting Report"
author: "Matthew Bond"
output: html_document
---

``` {r, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(plotly)

shooting_data <- read.csv("data/Mass-Shooting-Data.csv")

#Summary Information
total_shootings <- nrow(shooting_data)
total_killed <- sum(shooting_data$killed, na.rm = FALSE)
total_injured <- sum(shooting_data$injured, na.rm = FALSE)

shooting_summary <- group_by(shooting_data, state) %>% 
          summarise("Number of Shootings" = n(), "People Killed" = sum(killed), "People Injured" = sum(injured))
shooting_summary_table <- kable(shooting_summary, caption = "Shooting Statistics by State")
number_of_states <- nrow(shooting_summary)
state_shootings_count <- count(shooting_data, state)
state_most_shootings <- as.character(state_shootings_count$state[state_shootings_count$n == max(state_shootings_count$n)])
```

With mass shootings becoming a common occurance throughout the USA it is becoming more and more important to track when and where these acts of violence are taking place. In 2015 there were `r total_shootings` shootings that took a total of `r total_killed` lives. In addition to those `r total_killed`, another `r total_injured` people were injured in these tragic events. These shootings took place in `r number_of_states` states with `r state_most_shootings` having the most shootings.

`r shooting_summary_table`

``` {r, echo=FALSE}
#Description of particular incident
worst_shooting_city <- as.character(shooting_data$city[shooting_data$killed == max(shooting_data$killed)])
worst_shooting_killed <- shooting_data$killed[shooting_data$killed == max(shooting_data$killed)]
worst_shooting_injured <- shooting_data$injured[shooting_data$killed == max(shooting_data$killed)]
worst_shooting_date <- as.character(shooting_data$date[shooting_data$killed == max(shooting_data$killed)])
```

The single worst attack took place on `r worst_shooting_date` in `r worst_shooting_city`, `r worst_shooting_killed` people were killed and `r worst_shooting_injured` were injured.

``` {r, echo=FALSE, message=FALSE, warning=FALSE}
# Interactive Map
map_stats <- shooting_data

map_stats$hover <- paste(map_stats$city, "<br>Killed: ", map_stats$killed, "<br>Injured: ", map_stats$injured)

Month <- c("January", "Febuary", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")


g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("grey85"),
  subunitwidth = 1,
  countrywidth = 1,
  subunitcolor = toRGB("black"),
  countrycolor = toRGB("black")
)

plot_ly(map_stats, lon = lng, lat = lat, text = hover,
        marker = list(size = (killed + injured)),
        color = killed, type = 'scattergeo', locationmode = 'USA-states') %>%
layout(title = "2015 Shootings", geo = g)  

#Interactive Plot
months <- shooting_data
months$date <- as.Date(months$date, "%B %d, %Y")
months$date <- as.character(months$date, format = "%m")
months <- group_by(months, date) %>% summarise(sum(killed), sum(injured))
Casualties <- c(months$`sum(killed)`)

month_data <- plot_ly(
  x = Month,  
  y = Casualties,
  name = "Killed",
  type = "bar",
  filename="r-docs/month-bar-graph"
)

month_data2 <- add_trace(
  month_data,
  x = c("January", "Febuary", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"), 
  y = c(months$`sum(injured)`),
  name = "Injured",
  filename="r-docs/month-bar-graph"
)

layout(title = "2015 Shootings Casualties by Month", month_data2, barmode = "stack")
```







